### 2021-04-19 conclusion.tex
Add todos based on reviews 1 and 2 (excluding Minor comments)
Improve the paragraph discussing KBO weights
Resolves a comment from R2.

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help designing new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these pattern to a human-understandable form.

\gls{kbo}, that we choose in our experiments, is in addition to a symbol precedence
also determined by symbol \emph{weights} (we kept these fixed to the default value 1 in this work).
Learning to recommend also the symbol weights in addition to the precedences
represents an interesting avenue for future research.

>>>>

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help designing new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these pattern to a human-understandable form.
\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}

In addition to the symbol precedence,
\gls{kbo} is determined by symbol \emph{weights}.
In this work, we kept the symbol weights fixed to the value 1.
Learning to recommend symbol weights in addition to the precedences
represents an interesting avenue for future research.
